---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# plusraster

<!-- badges: start -->
<!-- badges: end -->

The goal of plusraster is to fast plot raster images in ggplot2. There is a `plus_raster()` function that works like `image()` for single-layer rasters or like `plotRGB()` for 3 or 4 layer rasters. Because we use raster annotation, we must set the xlim and ylim separately (or have it already set up by other data). 

(I'm still working my way around gg layers, surely we can grab the extent to do this and/or inherit from the input gg upstream). 

## Installation

You can install the development version: 

``` r
## install.packages("remotes")
remotes::install_github("mdsumner/plusraster")
```

## Example


```{r example}
library(plusraster)
library(raster)
library(ggplot2)

topo <- quadmesh::etopo

gg <- ggplot() + xlim(-180, 180) + ylim(-90, 0)

gg + plus_raster(topo, col = viridis::viridis(100), breaks = seq(-8000, 5000, length.out = 12)) 
gg + plus_raster(topo, col = viridis::viridis(100), breaks = quantile(topo, seq(0, 1,length.out = 15))) 

gg + plus_raster(topo, breaks = seq(0, 1000, length.out = 10), alpha = 0.2)


f <- system.file("external/rlogo.grd", package="raster")
ggplot() + plus_raster(lazyraster::lazyraster(f)) + xlim(0, 101) + ylim(0, 77)



library(ceramic)
ceramic_key <- "pk.eyJ1IjoibWRzdW1uZXIiLCJhIjoiY2p0bDI1aGY1MTRiNDQ0bWR2djh4dzgxOSJ9.zPM71aZwRWHc9U5kvDQDIA"
Sys.setenv(MAPBOX_API_KEY=ceramic_key)

cc <- cc_location(raster::extent(147.3, 147.35, -42.89, -42.87), zoom = 15)
g2 <- ggplot() + xlim(raster::xmin(cc), 
                      raster::xmax(cc)) + ylim(raster::ymin(cc), raster::ymax(cc)) + 
  plus_raster(cc, alpha = 0.9) + 
  coord_equal()
print(g2)

## transparency can be per cell, but note this is transpose/flip orientation 
g3 <- ggplot() + xlim(raster::xmin(cc), 
                      raster::xmax(cc)) + ylim(raster::ymin(cc), raster::ymax(cc)) + 
  plus_raster(cc, alpha = rep(c(0.2, 0.6), each = ncell(cc)/2)) + 
  coord_equal()
print(g3)




```

---

Please note that the 'plusraster' project is released with a
[Contributor Code of Conduct](https://github.com/mdsumner/plusraster/blob/master/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
