---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
ceramic_key <- Sys.getenv("MAPBOX_API_KEY")
```
# plusraster

<!-- badges: start -->
<!-- badges: end -->

The goal of plusraster is to fast plot raster images in ggplot2. There is a `plus_raster()` function that works like `image()` for single-layer rasters or like `plotRGB()` for 3 or 4 layer raster. 


## Installation

You can install the development version: 

``` r
## install.packages("remotes")
remotes::install_github("mdsumner/plusraster")
```

## Example


```{r example}
library(plusraster)
library(raster)
library(ggplot2)

topo <- quadmesh::etopo

gg <- ggplot() + xlim(-180, 180) + ylim(-90, 0)

gg + plus_raster(topo, col = viridis::viridis(100), breaks = seq(-8000, 5000, length.out = 12)) 
gg + plus_raster(topo, col = viridis::viridis(100), breaks = quantile(topo, seq(0, 1,length.out = 15))) 

gg + plus_raster(topo, breaks = seq(0, 1000, length.out = 10), alpha = 0.2)


f <- system.file("external/rlogo.grd", package="raster")
# ggplot() + plus_raster(lazyraster::lazyraster(f)) + xlim(0, 101) + ylim(0, 77)

ggplot() + plus_raster(raster(f), interpolate = FALSE) + xlim(20, 50) + ylim(20, 40)
## underlying rasterImage interpolation is available
ggplot() + plus_raster(raster(f), interpolate = TRUE) + xlim(20, 50) + ylim(20, 40)


library(ceramic)

## you need your own key here
## ceramic_key <- "<your key>" ## see ?ceramic::get_api_key
Sys.setenv(MAPBOX_API_KEY=ceramic_key)

cc <- cc_location(raster::extent(147.3, 147.35, -42.89, -42.87), zoom = 15)
g2 <- ggplot() + xlim(raster::xmin(cc), 
                      raster::xmax(cc)) + ylim(raster::ymin(cc), raster::ymax(cc)) + 
  plus_raster(cc, alpha = 0.9) + 
  coord_equal()
print(g2)

## transparency can be per cell, but note this is transpose/flip orientation 
g3 <- ggplot() + xlim(raster::xmin(cc), 
                      raster::xmax(cc)) + ylim(raster::ymin(cc), raster::ymax(cc)) + 
  plus_raster(cc, alpha = rep(c(0.2, 0.6), each = ncell(cc)/2)) + 
  coord_equal()
print(g3)




```


## Timings

```{r timings}
big <- quadmesh::etopo #raster::disaggregate(quadmesh::etopo, fact = 4)

system.time({
pr <- ggplot() + xlim(-180, 180) + ylim(-90, 0) + 
  plus_raster(big, col = colorRampPalette(scales::brewer_pal()(9)[9:5])(26))
                             print(pr)
})



system.time({
  dr <- ggplot(as.data.frame(big, xy = TRUE), aes(x, y, fill = layer)) + geom_raster()
  
  print(dr)
})


```


## VERY EXPERIMENTAL

```{r expr}
ggplot(big) 

ggplot(big) + coord_equal() + geom_sf(data = sf::st_as_sf(raster::rasterToContour(big)))


ggplot(cc) + coord_equal()



ggplot(big) + xlim(100, 150)

## the dummy points get cropped so warning
ggplot(big) + coord_equal() + ylim(-70, -30) + xlim(150, 250)





```
---

Please note that the 'plusraster' project is released with a
[Contributor Code of Conduct](https://github.com/mdsumner/plusraster/blob/master/CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
